Near Optimal Behavior via Approximate State Abstraction

### 2016-05-26 paper/example_domains.tex
removing minefield

% Description of visuals.
We provide visuals of both the ground \ac{MDP} and resulting abstract \ac{MDP} for one domain. A grey circle indicates a state and colored arrows indicate transitions. The thickness of the arrow indicates how much reward is associated with that transition. In the ground \acp{MDP}, states are labeled with a number. In the abstract \acp{MDP}, we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their ground states. %(some are visually unwieldy and so were not labelled).

%Description of code base
Our code base\footnote{Available here: \url{github.com/david-abel/state_abstraction}} provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}. We use the graph-visualization library GraphStream~\cite{graphstream} and the planning and \ac{RL} library, BURLAP\footnote{http://burlap.cs.brown.edu/}. For all experiments, we set $\gamma$ to $0.95$.

@@

% Subsection: Minefield.
%\subsection{Minefield}
Minefield is a test problem we are introducing that uses the Grid World dynamics of \citet{russell1995modern} with slip probability of $x$. The reward function is such that moving up in the top row of the grid receives $1.0$ reward; all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward. (These are the states with ``mines'' in them.) We set $N=10, M=4, \varepsilon=0.5, \kappa = 5, x = 0.01$. We depict the original Minefield and an abstract Minefield in Figure \ref{fig:minefield-vis}.

% Minefield Compression Visuals
\begin{figure}
\centering
\subfigure[Ground Minefield]{
\includegraphics[width=0.34\columnwidth]{figures/ground_minefield.png}}
\subfigure[Abstract Minefield]{
\includegraphics[width=0.34\columnwidth]{figures/abs_minefield.png}}
\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $
\varepsilon=0.5$}
\label{fig:minefield-vis}
\end{figure}

% Subsection: Random.
%\subsection{Random}

In the Random \ac{MDP} domain we consider, there are $100$ states and $3$ actions. For each state, each action transitions to one of two randomly selected states with probability $0.5$.

>>>>

% Description of visuals.
%We provide visuals of both the ground \ac{MDP} and resulting abstract \ac{MDP} for one domain. A grey circle indicates a state and colored arrows indicate transitions. The thickness of the arrow indicates how much reward is associated with that transition. In the ground \acp{MDP}, states are labeled with a number. In the abstract \acp{MDP}, we indicate which ground states were collapsed to each abstract state by labelling the abstract states with their ground states. %(some are visually unwieldy and so were not labelled).

%Description of code base
Our code base\footnote{\url{github.com/david-abel/state_abstraction}} provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}. We use the graph-visualization library GraphStream~\cite{graphstream} and the planning and \ac{RL} library, BURLAP\footnote{http://burlap.cs.brown.edu/}. For all experiments, we set $\gamma$ to $0.95$.

@@

% Subsection: Minefield.
%\subsection{Minefield}
Minefield is a test problem we are introducing that uses the Grid World dynamics of \citet{russell1995modern} with slip probability of $x$. The reward function is such that moving up in the top row of the grid receives $1.0$ reward; all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward. (These are the states with ``mines'' in them.) We set $N=10, M=4, \varepsilon=0.5, \kappa = 5, x = 0.01$.
% Minefield Compression Visuals
%\begin{figure}
%\centering
%\subfigure[Ground Minefield]{
%\includegraphics[width=0.3\columnwidth]{figures/ground_minefield.png}}
%\subfigure[Abstract Minefield]{
%\includegraphics[width=0.34\columnwidth]{figures/abs_minefield.png}}
%\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $
%\varepsilon=0.5$}
%\label{fig:minefield-vis}
%\end{figure} 
% Subsection: Random.
%\subsection{Random}
In the Random \ac{MDP} domain we consider, there are $100$ states and $3$ actions. For each state, each action transitions to one of two randomly selected states with probability $0.5$.
